Profiles of Wind Veer and Wind Speed in Turbulent Ekman Flow

### 2024-07-18 write1/manuscript.tex
added data citations to part I

% additional packages
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{booktabs} 
\usepackage{amssymb}
\usepackage{hyperref}
\setcitestyle{aysep={}}
\linenumbers

@@

@@

  \includegraphics[width=0.5\textwidth]{../plot/c_log.pdf}
  \caption{c-log.
    \label{fig:clog}}

@@

  \phantom{AAA}\textbf{(a)\hspace{0.3\textwidth}(b)\hspace{0.3\textwidth}(c)}\\
  \includegraphics[width=\textwidth]{../plot/ekman_profiles.pdf}
  \caption{ \textbf{(a)} Velocity deficity, \textbf{(b)} velocity profile in shear-aligned hodographs and \textbf{(c)} hodograph in geostrophy-aligned coordinates.
    Thick, solid lines show theory, dashed lines data from DNS. }
  \label{fig:hodograph} 

@@

@@

\textbf{Compare} to van Driest scaling

\textbf{Remember} of interpretation in the context of eddy viscosity (Fig.~\ref{fig:stresses}) 
Consider Townsend ``Turbulent Shear Flow''  Chapter 7.18: p. 319 
%
\par%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
Implications for \textbf{K-theory} (we now can consider that shear and stress are not necessarily perfectly aligned).
$\rightarrow$ can we do something to infer a K-profile from these theoretical considerations? 
%
\begin{figure}
  \includegraphics[width=\textwidth]{../plot/mag_dir.pdf} 
  \caption{Total velocity and veering (in degrees) vs inner and outer height.
    Dashed lines show DNS data, thick lines are from semi-empirical theory.} 
\end{figure} 
%
\section{Conclusions}
%
Applications:
\begin{itemize}
\item reference-shear for neutral profile approaches(systematic!) $\rightarrow$ wind engineering! 
\item initial condition for LES/DNS to eliminate/minimize inertial oscillation in Benchmark simulations
\item
\end{itemize}

>>>>

% additional packages
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{booktabs} 
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{caption}
\setcitestyle{aysep={}}
\linenumbers

@@

  \label{eqn:abc_log}

@@

  \centerline{\includegraphics[width=0.5\textwidth]{../plot/c_log.pdf}}
  \caption{Coefficients $a_\text{log}$, $b_\text{log}$ and $c_\log$ (cf. Eq.~\ref{eqn:abc_log}) as a function of 
    the viscous Reynolds number $Re_D$. The approximate range of scale separation relevant for atmospheric application 
    is found in between the dotted lines, where $a_\text{log}\simeq 0$ and $c_\text{log})\simeq 0.4$ }
  \label{fig:clog}

@@

@@

An alternative approach that considers viscous effects close to the surface is the van-Driest scaling \citep{vandriest:JOT1956}, 
where an exponential damping of Prandtl's mixing length is considered near the wall to yield 
\begin{align}
  \frac{\p u^+}{\p y^+} = \frac{2}{ 1+ \sqrt{1+\left(2\kappa y^+\right)^2 (1-\exp\left[-y^+\right])}};
\end{align}
the spanwise component is zero as no rotational effects are considered. 
%
Comparing our proposed formulation for the stream-wise velocity in the inner layer to  \citeauthor{vandriest:JOT1956}'s formulation 
yields later convergence of the velocity onto the logarithmic profile while, over all, it serves as an excellent model of the streamwise 
velocity component:
% 
Notable deviations (on the order of few percent) only occur in the region $10 < z^+ < 30$, 
where the velocity transitions from the linear to the logarithmic profile. 
\begin{figure}
  \centerline{\includegraphics[width=0.66\textwidth]{../plot/vanDriest_profile.png}}
  \caption{Near-wall velocity profile according to the 
    van-Driest scaling (blue, solid) in comparison with 
    the present model (red, dashed), 
    the viscous law of the wall (orange dashed), and 
    the logarithmic law (green, solid)} 
  \label{fig:vanDriest}
\end{figure}

@@

\textbf{Remember} of interpretation in the context of eddy viscosity (Fig.~\ref{fig:stresses}) 
Consider Townsend ``Turbulent Shear Flow''  Chapter 7.18: p. 319 
%
\begin{figure}
  \phantom{AAA}\textbf{(a)\hspace{0.3\textwidth}(b)\hspace{0.3\textwidth}(c)}\\
  \includegraphics[width=\textwidth]{../plot/ekman_profiles.pdf}
  \caption{ \textbf{(a)} Velocity deficity, \textbf{(b)} velocity profile in shear-aligned hodographs and \textbf{(c)} hodograph in geostrophy-aligned coordinates.
    Thick, solid lines show theory, dashed lines data from DNS. }
  \label{fig:hodograph} 
\end{figure}

%
\par%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
Implications for \textbf{K-theory} (we now can consider that shear and stress are not necessarily perfectly aligned).
$\rightarrow$ can we do something to infer a K-profile from these theoretical considerations? 
%
\begin{figure}
  \includegraphics[width=\textwidth]{../plot/mag_dir.pdf} 
  \caption{Total velocity and veering (in degrees) vs inner and outer height.
    Dashed lines show DNS data, thick lines are from semi-empirical theory.} 
\end{figure} 
%
\section{Conclusions}
%
Applications:
\begin{itemize}
\item reference-shear for neutral profile approaches(systematic!) $\rightarrow$ wind engineering! 
\item initial condition for LES/DNS to eliminate/minimize inertial oscillation in Benchmark simulations
\item
\end{itemize}
